---
title: "Fingerprint Data Frame"
author: "Marta García"
date: "July 9, 2017"
output: html_document
---
### The data frame will have 6 columns:
- participant name
- question (number 1:10 and letter A-E)
- treatment (one to one or one to many)
- response per question (T/F, 1/0)
- grade per question (T/F)
- order of tests administered (1:10)

### This code will create 10 data frames (one per participant) and then stack all 10 to create the final data frame.

We will create a vector for question and for the solutions 
and then reuse it per data frame since it is constant per person.
```{r}
# vector question will be used as column 2 in every data frame
question <- c("1A", "1B", "1C", "1D", "1E",
              "2A", "2B", "2C", "2D", "2E",
              "3A", "3B", "3C", "3D", "3E",
              "4A", "4B", "4C", "4D", "4E",
              "5A", "5B", "5C", "5D", "5E",
              "6A", "6B", "6C", "6D", "6E",
              "7A", "7B", "7C", "7D", "7E",
              "8A", "8B", "8C", "8D", "8E",
              "9A", "9B", "9C", "9D", "9E",
              "10A", "10B", "10C", "10D", "10E")

# vector answer_key are the answers to questions
# will run later again participant responses to see if participant answered question correctly
answer_key <- c(0, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 1, 0, 0,
                0, 0, 0, 1, 0,
                0, 1, 0, 0, 0,
                0, 1, 1, 0, 0,
                1, 0, 0, 0, 1,
                1, 1, 0, 0, 1,
                1, 0, 0, 1, 1,
                1, 0, 1, 0, 1)
length(answer_key)
```
### PARTICIPANT 1: Sarah Kline
```{r}
# participant_1 is col 1, participant name
# rep() to repeat name 50 times
participant_1 <- rep("Sarah Kline", 50)

# treatment_1 is col 2, treatment level
# rep() to repeat 5 times per test
# length() = 50 since there are 50 entries
treatment_1 <- rep(c("one to one", "one to many", "one to one",
                 "one to one", "one to many", "one to one",
                 "one to many", "one to many", "one to one",
                 "one to many"), each = 5)
length(treatment_1)

# responses_1 is col 4, participant answer per question (1/0 for T/F)
# if a participant answered that fingerprint is a match, input 1, otherwise 0
# length() = 50 since there are 50 entries
## values are placeholders until we get results
responses_1 <- c(1, 0, 1, 0, 0,
                 0, 1, 0, 0, 1,
                 0, 0, 0, 1, 0,
                 1, 0, 0, 1, 1,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 1,
                 1, 1, 0, 0, 1,
                 0, 0, 0, 1, 1,
                 1, 0, 1, 1, 0)
length(responses_1)

# if a participant answered correctly, input 1, otherwise 0
# length() = 50 since there are 50 entries
## values are placeholders until we get results
# grade_1 <- c(1, 0, 0, 1, 1,
#              0, 0, 0, 0, 0,
#              1, 1, 1, 0, 1,
#              1, 0, 0, 1, 0,
#              1, 0, 0, 1, 1,
#              0, 0, 0, 1, 1,
#              0, 0, 1, 1, 0,
#              0, 1, 0, 1, 0,
#              1, 1, 1, 1, 1,
#              1, 1, 1, 0, 0)
# length(grade_1)

# grade_1 is col 5, participant grade per question (T/F)
# set == and if participant answered correctly will output TRUE 
grade_1 <- as.numeric(responses_1 == answer_key)

# order_1 is col 6, order of tests administered
# rep() to repeat 5 times per test

# 1,2,3,4,5,6,7,8,9,10
# 9,1,3,6,4,8,7,5,10,2
order_1 <- rep(c(2, 10, 3, 5, 8, 4, 7, 6, 1, 9), each = 5)

# renaming col 1, 3:6
# data.frame() to create dataframe of 6 columns
# View() to check if sarah_df is correct
sarah_df <- data.frame(participant = participant_1, 
                       question, 
                       treatment = treatment_1,
                       response = responses_1,
                       grade = grade_1,
                       order = order_1)

```
### PARTICIPANT 2: Jake Howell
```{r}
participant_2 <- rep("Jake Howell", 50)

treatment_2 <- rep(c("one to many", "one to one", "one to many",
                     "one to many", "one to one", "one to many",
                     "one to one", "one to one", "one to many",
                     "one to one"), each = 5)

responses_2 <- c(0, 0, 0, 1, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 1, 0, 0, 0, 0,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 1,
                 0, 1, 0, 0, 1,
                 0, 0, 0, 0, 0,
                 1, 0, 1, 0, 1)
length(responses_2)


grade_2 <- as.numeric(responses_2 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 1,6,3,7,5,8,9,2,10,4
order_2 <- rep(c(1, 8, 3, 10, 5, 2, 4, 6, 7, 9), each = 5)

jake_df <- data.frame(participant = participant_2,
                      question,
                      treatment = treatment_2,
                      response = responses_2,
                      grade = grade_2,
                      order = order_2)

```
### PARTICIPANT 3: Joshua Core
```{r}
participant_3 <- rep("Joshua Core", 50)

treatment_3 <- rep(c("one to one", "one to many", "one to one",
                     "one to many", "one to one", "one to one",
                     "one to many", "one to many", "one to one",
                     "one to many"), each = 5)

responses_3 <- c(0, 0, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 1, 0,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 0, 0, 0, 0, 1,
                 1, 1, 0, 0, 1,
                 0, 0, 0, 0, 0,
                 1, 0, 1, 0, 1)
length(responses_3)

grade_3 <- as.numeric(responses_3 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 3,2,6,9,7,5,4,8,10,1
order_3 <- rep(c(10, 2, 1, 7, 6, 3, 5, 8, 4, 9), each = 5)

josh_df <- data.frame(participant = participant_3,
                      question,
                      treatment = treatment_3,
                      response = responses_3,
                      grade = grade_3,
                      order = order_3)

```
### PARTICIPANT 4: Emanuelle Alemar
```{r}
participant_4 <- rep("Emanuelle Alemar", 50)

treatment_4 <- rep(c("one to many", "one to one", "one to many",
                     "one to one", "one to many", "one to many",
                     "one to one", "one to one", "one to many",
                     "one to one"), each = 5)

responses_4 <- c(0, 0, 1, 0, 0,
                 0, 1, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 1, 0,
                 0, 1, 0, 0, 0,
                 1, 1, 1, 0, 0,
                 0, 0, 0, 0, 1,
                 0, 1, 0, 0, 0,
                 1, 0, 0, 1, 1,
                 0, 0, 1, 0, 0)

grade_4 <- as.numeric(responses_4 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 7,4,5,10,8,6,1,2,9,3
order_4 <- rep(c(7, 8, 10, 2, 3, 6, 1, 5, 9, 4), each = 5)

emanuelle_df <- data.frame(participant = participant_4,
                           question,
                           treatment = treatment_4,
                           response = responses_4,
                           grade = grade_4,
                           order = order_4)

```
### PARTICIPANT 5: Mishal McNeill
```{r}
participant_5 <- rep("Mishal McNeill", 50)

treatment_5 <- rep(c("one to one", "one to many", "one to many",
                     "one to many", "one to many", "one to many",
                     "one to one", "one to one", "one to one",
                     "one to one"), each = 5)

responses_5 <- c(0, 0, 0, 0, 0,
                 0, 1, 0, 0, 1,
                 1, 1, 1, 1, 0,
                 1, 0, 0, 1, 0,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 0,
                 1, 1, 0, 0, 1,
                 1, 0, 0, 1, 1,
                 1, 0, 1, 0, 1)

grade_5 <- as.numeric(responses_5 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 4,6,10,5,1,8,9,2,7,3
order_5 <- rep(c(5, 8, 10, 1, 4, 2, 9, 6, 7, 3), each = 5)

mishal_df <- data.frame(participant = participant_5,
                        question,
                        treatment = treatment_5,
                        response = responses_5,
                        grade = grade_5,
                        order = order_5)

```
### PARTICIPANT 6: Jonathan Che
```{r}
participant_6 <- rep("Jonathan Che", 50)

treatment_6 <- rep(c("one to many", "one to one", "one to one",
                     "one to one", "one to one", "one to one",
                     "one to many", "one to many", "one to many",
                     "one to many"), each = 5)

responses_6 <- c(1, 0, 1, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 1, 0, 1, 1,
                 0, 0, 0, 1, 0,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 1,
                 1, 1, 0, 0, 1,
                 1, 0, 0, 0, 0,
                 1, 0, 1, 0, 1)

grade_6 <- as.numeric(responses_6 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 9,7,6,1,5,8,4,10,3,2
order_6 <- rep(c(4, 10, 9, 7, 5, 3, 2, 6, 1, 8), each = 5)

jonathan_df <- data.frame(participant = participant_6,
                          question,
                          treatment = treatment_6,
                          response = responses_6,
                          grade = grade_6,
                          order = order_6)

```
### PARTICIPANT 7: Chris Bryant
```{r}
participant_7 <- rep("Chris Bryant", 50)

treatment_7 <- rep(c("one to one", "one to many", "one to many",
                     "one to one", "one to many", "one to many",
                     "one to many", "one to one", "one to one",
                     "one to one"), each = 5)

responses_7 <- c(0, 0, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 0, 1, 0,
                 0, 0, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 1,
                 1, 0, 0, 0, 1,
                 0, 0, 0, 0, 0,
                 1, 0, 1, 0, 1)

grade_7 <- as.numeric(responses_7 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 5,8,7,1,6,4,10,3,2,9
order_7 <- rep(c(4, 9, 8, 6, 1, 5, 3, 2, 10, 7), each = 5)

chris_df <- data.frame(participant = participant_7,
                       treatment = treatment_7,
                       question,
                       response = responses_7,
                       grade = grade_7,
                       order = order_7)
```
### PARTICIPANT 8: Kristyn Frisque
```{r}
participant_8 <- rep("Kristyn Frisque", 50)

treatment_8 <- rep(c("one to many", "one to one", "one to one",
                     "one to many", "one to one", "one to one",
                     "one to one", "one to many", "one to many",
                     "one to many"), each = 5)

responses_8 <- c(0, 0, 1, 0, 0,
                 0, 0, 0, 0, 0,
                 1, 0, 0, 0, 0,
                 1, 0, 0, 0, 1,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 0, 0, 0, 0, 1,
                 1, 1, 0, 0, 0,
                 0, 0, 0, 0, 0,
                 0, 0, 1, 0, 1)

grade_8 <- as.numeric(responses_8 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 10,7,2,5,3,9,8,1,4,6
order_8 <- rep(c(8, 3, 5, 9, 4, 10, 2, 7, 6, 1), each = 5)

kristyn_df <- data.frame(participant = participant_8,
                         treatment = treatment_8,
                         question,
                         response = responses_8,
                         grade = grade_8,
                         order = order_8)
```
### PARTICIPANT 9: Cieran Evans
```{r}
participant_9 <- rep("Cieran Evans", 50)

treatment_9 <- rep(c("one to many", "one to one", "one to many",
                     "one to many", "one to many", "one to many",
                     "one to one", "one to one", "one to one",
                     "one to one"), each = 5)
responses_9 <- c(1, 0, 0, 0, 1,
                 0, 0, 0, 0, 0,
                 1, 1, 1, 1, 1,
                 1, 0, 0, 1, 1,
                 0, 1, 0, 0, 0,
                 0, 1, 1, 0, 0,
                 1, 0, 0, 0, 1,
                 1, 1, 0, 0, 1,
                 0, 0, 0, 0, 1,
                 1, 0, 1, 0, 1)

grade_9 <- as.numeric(responses_9 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 1,9,8,6,10,3,7,5,2,4
order_9 <- rep(c(1, 9, 6, 10, 8, 4, 7, 3, 2, 5))

cieran_df <- data.frame(participant = participant_9,
                      treatment = treatment_9,
                      question,
                      response = responses_9,
                      grade = grade_9,
                      order = order_9)
```
### PARTICIPANT 10: Niccolo Dalmasso
```{r}
participant_10 <- rep("Niccolo Dalmasso", 50)

treatment_10 <- rep(c("one to one", "one to many", "one to one",
                      "one to one", "one to one", "one to one",
                      "one to many", "one to many", "one to many",
                      "one to many"), each = 5)

responses_10 <- c(0, 1, 0, 0, 0,
                  0, 0, 0, 1, 0,
                  1, 1, 1, 0, 0,
                  0, 0, 0, 1, 1,
                  0, 1, 0, 0, 0,
                  0, 1, 1, 0, 0,
                  1, 0, 0, 0, 0,
                  1, 1, 0, 0, 1,
                  0, 0, 0, 1, 1,
                  1, 0, 1, 0, 0)

grade_10 <- as.numeric(responses_10 == answer_key)

# 1,2,3,4,5,6,7,8,9,10
# 10,1,4,9,8,2,6,5,7,3
order_10 <- rep(c(2, 6, 10, 3, 8, 7, 9, 5, 4, 1), each = 5)

niccolo_df <- data.frame(participant = participant_10,
                     treatment = treatment_10,
                     question,
                     response = responses_10,
                     grade = grade_10,
                     order = order_10)
```


### using rbind() to stack the individual participant data frames
```{r}
exp_fingerprint_data <- rbind(sarah_df, jake_df, josh_df, 
                        emanuelle_df, mishal_df, jonathan_df,
                        chris_df, kristyn_df, cieran_df,
                        niccolo_df)
View(exp_fingerprint_data)

# this line will save as dataframe, as a .RData
save(exp_fingerprint_data, file = "exp_fingerprint_data.RData")

# eventually we should save as .RData
```

